### 2017-12-04 paper/sexSelectionSpacing-ver1.tex

@@

Table \ref{tab:median_sex_ratio_low} shows the predictions for women 
with no education.
Overall, spacing is shorter the fewer boys a couple has, but the
differences in median duration are never more than 3 months and most
are only one or two months
(the exceptions to this pattern are mostly for small cells).
Furthermore, although the median duration generally increases over 
time---with the exception of the first spell---there is little 
change in the relative pattern of durations across sex compositions
over time.
These results point to an absence of sex-selective abortions for 
this group of women, which is also supported by the fact that
most of the predicted sex ratios are close to the natural sex ratio.%
\footnote{
I return to whether there are statistically significant 
differences below when examining sex ratios within spells.
}

@@

>>>>

[Difference in approach: use the sex composition of prior
children, rather the sex of the last child.
Problem is that the cell sizes become too small if we further split up
the higher spell cells.

Define cell]

@@

Table \ref{tab:median_sex_ratio_low} shows the predictions for women 
with no education.
Overall, spacing is shorter the fewer boys a couple has, but the
differences in median duration are never more than 3 months and most
are only one or two months
(the exceptions to this pattern are mostly for small cells).
Furthermore, although the median duration generally increases over 
time---with the exception of the first spell---there is little 
change in the relative pattern of durations across sex compositions
over time.
These results point to an absence of sex-selective abortions for 
this group of women, which is supported by predicted sex ratios
that mostly close to the natural sex ratio.%
\footnote{
I return to whether there are statistically significant 
differences below when examining sex ratios within spells.
}

@@

For women with between 1 and 7 years of education it is harder
to discern a pattern, partly because a larger number of area,
sex composition, and periods combinations have relatively few 
births in them.
That said, the predicted median durations show less evidence 
of son preference than for women without education.
The exception to this are for the third spell for rural women
for the 1972-1984 and 1985-1994 periods where the median
durations are two and three months shorted with only girls
compared to only boys, although the duration is longer for
only girls in the 1995-2006 period.
As for women with no education, there is little evidence of
sex selection for women with 1 to 7 years of education,
consistent with the absence of changes in relative durations
across periods.
